%-------------------------------------------------------------------------------
%   SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%   CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {Amazon Development Centre London} % Organization
    {London, UK} % Location
    {Jan. 2014 - Present} % Date(s)
    {
      \begin{cventrysummary}
      My role at Amazon sees me work in the Instant Video department where I jointly
      develop a cross-platform native video player targeted to run on Smart TVs,
      set-top boxes and games consoles. The software is deployed globally and
      has approximately 1.5million users per week streaming 5million+ hours of
      content.
      \end{cventrysummary}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Headed development on a high-profile device, attending PM/senior leadership meetings to advise and guide on development estimations and technical feasibility.}
        \item {Wrote fully tested and peer-reviewed code using industry best practices and test driven development in order to keep software quality high.}
        \item {Worked on-site internationally with Amazon’s software partners to debug and aid in the device implementation process.}
        \item {Set up and implemented an end-to-end build, test and release system which is now utilised by many teams.}
        \item {Mentored junior engineers and attended hiring training.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developer Technology Engineer} % Job title
    {Imagination Technologies} % Organization
    {Kings Langley, UK} % Location
    {May 2011 - Jan. 2014} % Date(s)
    {
      \begin{cventrysummary}
      A world-leading silicon IP company developing hardware and software for 
      graphics and general-purpose processors. My position as a Developer 
      Technology Engineer saw me working on a range of projects from 
      multiplatform desktop tools and utilities to the development of graphics
      demos and tutorials for the freely available PowerVR Graphics SDK.
      \end{cventrysummary}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and optimised demos for many different Smartphone and embedded platforms including iOS and Android.}
        \item {Designed and developed desktop utility software with Qt which is provided to developers and hardware customers to aid in optimising and developing for PowerVR hardware.}
        \item {Supported developers with optimising and implementing graphics techniques tailored to the hardware.}
        \item {Responsible for the publicly available source code components of the SDK, being team lead for this module.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Games Programmer} % Job title
    {Tick Tock Games} % Organization
    {Wakefield, UK} % Location
    {Aug. 2009 - May 2011} % Date(s)
    {
      \begin{cventrysummary}
      A small independent computer games company developing software for mobile
      devices and embedded fitness machines distributed globally.
      \end{cventrysummary}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on several Smartphone platforms including iOS and Android, developing and performing conversions of titles between these systems. }
        \item {8+ marketplace releases including one top-20 sports game on Android for several weeks.}
        \item {Introduced many new technologies to the company including GLSL GPU shaders and optimised engine tools for improved Artist-Programmer pipeline efficiency.}
        \item {Contributed to game design documents and was heavily involved in the design process. }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
